# Introduction {#intro}

Conceptial diagrams are vital for understanding processes and developing incremetal science, however, there seems to be very few packages or other software that aligns with the literature in how and when these diagrams should be developed.

This book uses `R` and the core packages [`diagrammeR`](https://cran.r-project.org/web/packages/DiagrammeR/index.html).

```{r message=FALSE, warning=FALSE, include=FALSE}
library(DiagrammeR)
```

There is a great resource written by the author [here](https://rich-iannone.github.io/DiagrammeR/index.html) but I am still working out overall how the package in R works.
- A good explaination of the features [here](https://rich-iannone.github.io/DiagrammeR/index.html#features)

## Resources

The general concept of the package I am using is very simple but the code looks intemidating:

```{r echo=TRUE}
grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica]
  'box'; 'shape'

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  'shape2'; 'circles'

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  'join'; 'arrow'
  
  # several 'edge' statements
  join->arrow
}
")
```

## My notes

For example, you might like to think of a simple statistical regression with a single `y` and `x`as:

$$ y_i = \beta_0 + \beta_1(x_i) + error_i $$
And if this was to be diagramatically represented it could be describled like so with the following descriptions:

*1:* We are proposing that $y_i$ is directly effected by $x_i$.

```{r echo=FALSE}
grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica]
  y; x

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  error; 'b0' 
  
  # several 'edge' statements
  y->x; y->'b0'
}
")
```

### Examples

This info I think is interesting but haven't investigated it much yet.

### Math insert

Here is an example of inserting math equations into `diagrammeR` using mathJax??

```{r}
source("./R/cos-example.R", echo = TRUE)
```

### Kol but not working

```{r eval=FALSE, include=TRUE}
###
# Delete specific nodes
# from the graph using
# `delete_node()`
###

library(DiagrammeR)
library(magrittr)

# Create a graph with a central
# node and multiples of children nodes
graph <-
create_graph(graph_attrs =
               "output = visNetwork") %>%
  add_n_nodes(1, "A") %>%
  select_nodes %>%
  add_n_nodes_ws(3, "B") %>%
  clear_selection %>%
  select_nodes("type", "B") %>%
  add_n_nodes_ws(3, "C")

# View the graph
graph %>% render_graph
```

### Mixed models

Mixed models essentially start with sample mean differences between groups and then add additional complexity in favour of poor fitting models.

You can write out models and variable relationships using statistical equations such as:

$$ outcome = \beta_0 + \beta_1(sex_i)$$
where the variables can be collected either through direct questions or transformed data from the orginal questions. What does it look like in a diagram explaining how the variables are proposed to be similar? Example below:

```{r include = FALSE}
grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica]
  Q1; Q2; Q3; Q4; Q5; Q6

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  1; 2; 3; 4; 5; 6; 7; 8

  # several 'edge' statements
  Q1->1 Q1->2 Q1->3 Q2->4 Q3->A
  Q3->D Q5->A Q2->4 Q2->5 Q6->F
  E->6 4->6 5->7 6->7 3->8
}
")
```

For example you might think that generally individuals that ...

$$ outcome = \beta_0 + \beta_1(sex_i) + \beta(age_i) + error_i $$

```{r include=FALSE}
grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica]
  b0; b1; b2; error

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  sex; age; 
  
  # several 'edge' statements
  b1->sex; b2->age
}
")
```