# Software and Hardware {#comps}

This is a great question I have been playing around with to help learn how to use the `diagrammeR` package. The question is:
<br>
**What is the difference between software and hardware?**
<br>
```{r}
library(tidyverse)
library(kableExtra)
```

I thought that is was an obvious difference. Hardware is the stuff that makes the software work. 

For example, `RAM` is hardware, `word` is software?

```{r echo = FALSE, warnings = FALSE, messages=FALSE}
Hardware <- c("RAM", "CPU", "Processors")
Software <- c("R", "word", "excel")
comp.dat <- cbind(Software,Hardware)
comp.dat1 <- as.data.frame(comp.dat)
kable(comp.dat1, format = "markdown")
```

## Software {.tabset}

But the problem is when somebody knows the interface (software that uses many types of software). Examples of this are programs like `RStudio`, `vs-code` and other such programs. This is because they are a single piece of software that uses "heaps" of other software.

```{r echo = FALSE}
grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica,
        fill = grey50]
  Scrap

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  revtools; rmarkdown; report
  
  node [shape = triangle,
        fixedsize = true,
        width = 0.9] // sets as circles
  data

  # several 'edge' statements
  RStudio->GIT RStudio->R RStudio->Python R->Python GIT->www
}
")
```

But then each bit of software such as `GIT` and `R` can be accessed by many different types of software...so is `R` not just hardware then?

```{r}
grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica,
        fill = grey50]
  RStudio; 'vs-code'

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  R; GIT; Python
  node [shape = triangle,
        fixedsize = true,
        width = 0.9] // sets as circles
  www

  # several 'edge' statements
  RStudio->GIT RStudio->R RStudio->Python R->Python GIT->www
  'vs-code'->GIT 'vs-code'->R 'vs-code'->Python
}
")
```

And now the question becomes about the definition of what software and hardware are...

```{r}
Hardware <- c("RAM", "CPU", "Processors")
Software <- c("R", "word", "excel")
comp.dat <- cbind(Software,Hardware)
comp.dat1 <- as.data.frame(comp.dat)
kable(comp.dat1, format = "markdown")
```

### RStudio

But the problem is when somebody knows the interface (software that uses many types of software). Examples of this are programs like `RStudio`, `vs-code` and other such programs. This is because they are a single piece of software that uses "heaps" of other software.

```{r echo = FALSE}
grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica,
        fill = grey50]
  RStudio

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  R; GIT; Python
  node [shape = triangle,
        fixedsize = true,
        width = 0.9] // sets as circles
  www

  # several 'edge' statements
  RStudio->GIT RStudio->R RStudio->Python R->Python GIT->www
}
")
```

### 'vs-code'

But then each bit of software such as `GIT` and `R` can be accessed by many different types of software...so is `R` not just hardware then?

```{r echo=FALSE}
grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica,
        fill = grey50]
  'vs-code'

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  R; GIT; Python; Ruby
  
  node [shape = triangle,
        fixedsize = true,
        width = 0.9] // sets as circles
  www

  # several 'edge' statements
  'vs-code'->GIT 'vs-code'->R 'vs-code'->Python 'ruby'->www 'vs-code'->Ruby
}
")
```

### R

```{r echo=FALSE}
grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica,
        fill = grey50]
  'R'

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  R; tidyverse; Python
  
  node [shape = triangle,
        fixedsize = true,
        width = 0.9] // sets as circles
  dplyr; ggplot2; others

  # several 'edge' statements
  R->dplyr R->ggplot2 R->others
  tidyverse->ggplot2 tidyverse->dplyr
  R->Python
}
")
```

## Computer processes {.tabset}

### RStudio

This is an example of a piece of software. It needs your computer (hardware) to run so therefore it is software. Just the same as `R`....but not really.

#### A simple `Rscript`

```{r}
grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica,
        fill = grey50]
  RStudio

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  word; html; pdf; R
  
  node [shape = triangle,
        fixedsize = true,
        width = 0.9] // sets as circles
  www

  # several 'edge' statements
  RStudio->R R->word R->html R->pdf html->www
}
")
```

But this is not really what is happening. For example this is the `RMarkdown` figure for this process:

```{r}
grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica,
        fill = grey50]
  RMD; MD

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  word; html; pdf
  
  node [shape = triangle,
        fixedsize = true,
        width = 0.9] // sets as circles
  www

  # several 'edge' statements
  RMD->MD MD->word MD->html MD->pdf html->www 
}
")
```

### v3

```{r}
var <- c("scale","name","Q1.1","Q1.2","Q1.3","Q1.4","Q2.1","Q2.2","Q2.3","Q2.4","Q2.5","Q2.6","Q2.7","Q2.8","Q2.9","Q2.10","Q3.1","Q3.2","Q3.3","Q4.1","Q4.2","Q5.1","Q5.2","Q5.3")

# dat <- read.csv("./data/overall_dummy_data.csv")
# glimpse(dat)

grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica]
  Q1; Q2; Q3; Q4; Q5; error

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  1; 2; 3; 4; 5; 6; 7; 8

  # several 'edge' statements
  Q1->1 Q1->2 Q1->3 Q1->4 
  Q2->5 Q2->6 Q2->7 Q2->8 Q2->9 Q2->10 Q1->11 Q2->12 Q2->13 Q2->14
  Q3->15 Q3->16 Q3->17
  Q4->18 Q4->19
  Q5->20 Q5->21 Q5->22
  1->general 2->general 1->A 2->D 1->G 1->F
  E->6 4->V 5->C 6->H 3->M
}
")

```

### v4

```{r echo = FALSE}
grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica,
        fill = grey50]
  RStudio

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  R; GIT; Python
  node [shape = triangle,
        fixedsize = true,
        width = 0.9] // sets as circles
  www

  # several 'edge' statements
  RStudio->GIT RStudio->R RStudio->Python R->Python GIT->www
}
")
```