# Likert Scales {#likscale}

## The problem

```{r load_packfdbages, message=FALSE, warning=FALSE, include=FALSE}
library(DiagrammeR)
```

To build a sampling design that accounts for the issues and nature of data collection of foriegn bank movements using person-to-person == surveys.

## Method

Here we want to address the key objectives of our reseach by collecting data in an unbias and representative way. To understand the true underlying trends in the data a pilot study with a large enough sample is explored below.

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(DT)
```

Here we have a difficult question to address due to the bias in the data capture method. This is really interesting and challenging from a statistical prospective. This is also a problem that the qualitative approach fails to address (waiting to see what others say about this..?)

Here is a step-by-step to approach to this research in a quantativite way:

1. The questions are grouped into sets of questions that all address a general objective or question the research has. We can first see if these patterns are true for the responses. These are as follows:

```{r}
grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica]
  Q1; error

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  1; 2; 3; 4;

  # several 'edge' statements
  Q1->1 Q1->2 Q1->3 Q1->4 
  1->general 2->general 3->A 4->D 4->G 4->F
  E->3 4->V 1->C 2->H 3->M E ->error
}
")
```

There are several issues with this because the data collected is often non-normal and needs to be transformed. The first step however is to simply visualise the data in a way that we will also be fitting the statistical models.

```{r}
var <- c("scale","name","Q1.1","Q1.2","Q1.3","Q1.4","Q2.1","Q2.2","Q2.3","Q2.4","Q2.5","Q2.6","Q2.7","Q2.8","Q2.9","Q2.10","Q3.1","Q3.2","Q3.3","Q4.1","Q4.2","Q5.1","Q5.2","Q5.3")

# dat <- read.csv("./data/overall_dummy_data.csv")
# glimpse(dat)

grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica]
  Q1; Q2; Q3; Q4; Q5; error

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  1; 2; 3; 4; 5; 6; 7; 8

  # several 'edge' statements
  Q1->1 Q1->2 Q1->3 Q1->4 
  Q2->5 Q2->6 Q2->7 Q2->8 Q2->9 Q2->10 Q1->11 Q2->12 Q2->13 Q2->14
  Q3->15 Q3->16 Q3->17
  Q4->18 Q4->19
  Q5->20 Q5->21 Q5->22
  1->general 2->general 1->A 2->D 1->G 1->F
  E->6 4->V 5->C 6->H 3->M
}
")

```

There is some simple dataset transformations that can be done to make it easier to work with the data in the plotting functions.


```{r echo = FALSE}
grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica,
        fill = grey50]
  Q1; Q2; Q3; Q4; error

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  1; 2; 3; 4;

  # several 'edge' statements
  Q1->1 Q2->2 Q3->3 Q4->4 
  1->id 2->general 3->birth 4->location 4->time 4->space E->offspring 4->sex 1->age 2->size 3->status error->E
}
")
```

## Flow diagram

Here I think we should add the relationship to each question and the proposed hypothesis...