# Likert Scales {#likscale}

## The problem

```{r message=FALSE, warning=FALSE, include=FALSE}
library(DiagrammeR)
```

To build a sampling design that accounts for the issues and nature of data collection of foriegn bank movements using person-to-person == surveys.

## Method

Here we want to address the key objectives of our reseach by collecting data in an unbias and representative way. To understand the true underlying trends in the data a pilot study with a large enough sample is explored below.

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(DT)
```

Here we have a difficult question to address due to the bias in the data capture method. This is really interesting and challenging from a statistical prospective. This is also a problem that the qualitative approach fails to address (waiting to see what others say about this..?)

Here is a step-by-step to approach to this research in a quantativite way:

1. The questions are grouped into sets of questions that all address a general objective or question the research has. We can first see if these patterns are true for the responses. These are as follows:

```{r}
grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica]
  Q1; error

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  1; 2; 3; 4;

  # several 'edge' statements
  Q1->1 Q1->2 Q1->3 Q1->4 
  1->general 2->general 3->A 4->D 4->G 4->F
  E->3 4->V 1->C 2->H 3->M E ->error
}
")
```

There are several issues with this because the data collected is often non-normal and needs to be transformed. The first step however is to simply visualise the data in a way that we will also be fitting the statistical models.

```{r}
var <- c("scale","name","Q1.1","Q1.2","Q1.3","Q1.4","Q2.1","Q2.2","Q2.3","Q2.4","Q2.5","Q2.6","Q2.7","Q2.8","Q2.9","Q2.10","Q3.1","Q3.2","Q3.3","Q4.1","Q4.2","Q5.1","Q5.2","Q5.3")

# dat <- read.csv("./data/overall_dummy_data.csv")
# glimpse(dat)

grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica]
  Q1; Q2; Q3; Q4; Q5; error

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  1; 2; 3; 4; 5; 6; 7; 8

  # several 'edge' statements
  Q1->1 Q1->2 Q1->3 Q1->4 
  Q2->5 Q2->6 Q2->7 Q2->8 Q2->9 Q2->10 Q1->11 Q2->12 Q2->13 Q2->14
  Q3->15 Q3->16 Q3->17
  Q4->18 Q4->19
  Q5->20 Q5->21 Q5->22
  1->general 2->general 1->A 2->D 1->G 1->F
  E->6 4->V 5->C 6->H 3->M
}
")

```

There is some simple dataset transformations that can be done to make it easier to work with the data in the plotting functions.


```{r echo = FALSE}
grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica,
        fill = grey50]
  Q1; Q2; Q3; Q4; error

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  1; 2; 3; 4;

  # several 'edge' statements
  Q1->1 Q2->2 Q3->3 Q4->4 
  1->id 2->general 3->birth 4->location 4->time 4->space E->offspring 4->sex 1->age 2->size 3->status error->E
}
")
```

## Flow diagram {.tabset}

Here I think we should add the relationship to each question and the proposed hypothesis...

### v1

```{r}
grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica]
  Q1; error

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  1; 2; 3; 4;

  # several 'edge' statements
  Q1->1 Q1->2 Q1->3 Q1->4 
  1->general 2->general 3->A 4->D 4->G 4->F
  E->3 4->V 1->C 2->H 3->M E ->error
}
")
```

### v2 

A similar automatic report can be generated using by using the DIY_ANOVA app [here](https://pecostats.shinyapps.io/DIY_ANOVA/). It consists of a reduced version of the following report and sections.


```{r fig.height=4, fig.width=4, include = TRUE}
library(DiagrammeR)
# ?DiagrammeR
# grViz("
#   digraph {
#     layout = twopi
#     node [shape = circle]
#     Y -> {B} {C D}
#   }")
# par(mfrow = c(2,1))

grViz("
#add nodes
  digraph boxes_and_circles{
  node [shape = circle]
  Normality; No; Yes; NoTransform; Transform
  node [shape = square]
  lm;glm;shinyDIYanova
#edge statements
edge [arrowhead = none]
Normality->No
Normality->Yes
Yes->NoTransform
NoTransform->shinyDIYanova
No->Transform
Transform->lm
Transform->glm
  }"
)

```

```{r }
grViz("digraph flowchart {
      # node definitions with substituted label text
      node [fontname = Helvetica, shape = rectangle]        
      tab1 [label = '@@1']
      tab2 [label = '@@2']
      tab3 [label = '@@3']
      tab4 [label = '@@4']
      tab5 [label = '@@5']

      # edge definitions with the node IDs
      tab1 -> tab2 -> tab3 -> tab4 -> tab5;
      }

      [1]: 'Questionnaire sent to n=1000 participants'
      [2]: 'Participants responded to questionnaire n=850'
      [3]: 'Participants came to clinic for evaluation n=700'
      [4]: 'Participants eligible for the study n=600'
      [5]: 'Study sample n=600'
      ")

# note the whitespace is not important
DiagrammeR("
  graph LR
    A-->B
    A-->C
    C-->E
    B-->D
    C-->D
    D-->F
    E-->F
")

DiagrammeR("
   graph TB
   A-->B
   A-->C
   C-->E
   B-->D
   C-->D
   D-->F
   E-->F
")

DiagrammeR("graph LR;A(Rounded)-->B[Squared];B-->C{A Decision};
 C-->D[Square One];C-->E[Square Two];
 style A fill:#E5E25F;  style B fill:#87AB51; style C fill:#3C8937;
 style D fill:#23772C;  style E fill:#B6E6E6;"
)

# Load in the 'mtcars' dataset
data(mtcars)
connections <- sapply(
 1:ncol(mtcars)
  ,function(i) {
     paste0(
        i
      ,"(",colnames(mtcars)[i],")---"
      ,i,"-stats("
      ,paste0(
        names(summary(mtcars[,i]))
        ,": "
        ,unname(summary(mtcars[,i]))
        ,collapse="<br/>"
      )
      ,")"
   )
 }
)

DiagrammeR(
   paste0(
     "graph TD;", "\n",
     paste(connections, collapse = "\n"),"\n",
     "classDef column fill:#0001CC, stroke:#0D3FF3, stroke-width:1px;" ,"\n",
     "class ", paste0(1:length(connections), collapse = ","), " column;"
   )
 )

# also with DiagrammeR() you can use tags from htmltools
# just make sure to use class = "mermaid"
library(htmltools)
diagramSpec = "
graph LR;
  id1(Start)-->id2(Stop);
  style id1 fill:#f9f,stroke:#333,stroke-width:4px;
  style id2 fill:#ccf,stroke:#f66,stroke-width:2px,stroke-dasharray: 5, 5;
"
html_print(tagList(
  tags$h1("R + mermaid.js = Something Special")
  ,tags$pre(diagramSpec)
  ,tags$div(class="mermaid",diagramSpec)
  ,DiagrammeR()
))

# sequence diagrams
# Using this "How to Draw a Sequence Diagram"
#   http://www.cs.uku.fi/research/publications/reports/A-2003-1/page91.pdf
# draw some sequence diagrams with DiagrammeR

library(DiagrammeR)

DiagrammeR("
sequenceDiagram;
   customer->>ticket seller: ask for ticket;
   ticket seller->>database: seats;
   alt tickets available
     database->>ticket seller: ok;
     ticket seller->>customer: confirm;
     customer->>ticket seller: ok;
     ticket seller->>database: book a seat;
     ticket seller->>printer: print ticket;
   else sold out
     database->>ticket seller: none left;
     ticket seller->>customer:  sorry;
   end
")
```

### v3

```{r}
var <- c("scale","name","Q1.1","Q1.2","Q1.3","Q1.4","Q2.1","Q2.2","Q2.3","Q2.4","Q2.5","Q2.6","Q2.7","Q2.8","Q2.9","Q2.10","Q3.1","Q3.2","Q3.3","Q4.1","Q4.2","Q5.1","Q5.2","Q5.3")

# dat <- read.csv("./data/overall_dummy_data.csv")
# glimpse(dat)

grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica]
  Q1; Q2; Q3; Q4; Q5; error

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  1; 2; 3; 4; 5; 6; 7; 8

  # several 'edge' statements
  Q1->1 Q1->2 Q1->3 Q1->4 
  Q2->5 Q2->6 Q2->7 Q2->8 Q2->9 Q2->10 Q1->11 Q2->12 Q2->13 Q2->14
  Q3->15 Q3->16 Q3->17
  Q4->18 Q4->19
  Q5->20 Q5->21 Q5->22
  1->general 2->general 1->A 2->D 1->G 1->F
  E->6 4->V 5->C 6->H 3->M
}
")

```

### v4

```{r echo = FALSE}
grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica,
        fill = grey50]
  Q1; Q2; Q3; Q4; error

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  1; 2; 3; 4;

  # several 'edge' statements
  Q1->1 Q2->2 Q3->3 Q4->4 
  1->id 2->general 3->birth 4->location 4->time 4->space E->offspring 4->sex 1->age 2->size 3->status error->E
}
")
```
