# Mixed regression models {#mixed}

## Models {.tabset}

Mixed models essentially start with sample mean differences between groups and then add additional complexity in favour of poor fitting models.

You can write out models and variable relationships using statistical equations such as $y_i = \beta_0 + \beta_1(x_i)$ where the variables can be collected either through direct questions or transformed data from the orginal questions. What does it look like in a diagram explaining how the variables are proposed to be similar? Example below:

### Constant only

$$ outcome = \beta_0$$

```{r echo=FALSE}
grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica]
  Q1; Q2; Q3; Q4; Q5; Q6

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  1; 2; 3; 4; 5; 6; 7; 8

  # several 'edge' statements
  Q1->1 Q1->2 Q1->3 Q2->4 Q3->A
  Q3->D Q5->A Q2->4 Q2->5 Q6->F
  E->6 4->6 5->7 6->7 3->8
}
")
```

### Single predictor

$$ outcome = \beta_0 + \beta_1(sex_i)$$

```{r echo=FALSE}
grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica]
  Q1; Q2; Q3; Q4; Q5; Q6

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  1; 2; 3; 4; 5; 6; 7; 8

  # several 'edge' statements
  Q1->1 Q1->2 Q1->3 Q2->4 Q3->A
  Q3->D Q5->A Q2->4 Q2->5 Q6->F
  E->6 4->6 5->7 6->7 3->8
}
")
```

### Multi-level v1

For example you might think that generally individuals that ...

$$ outcome = \beta_0 + \beta_1(sex_i) + \beta(age_i) + error_i $$

```{r echo=FALSE}
grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica]
  b0; b1; b2; error

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  sex; age; 
  
  # several 'edge' statements
  b1->sex; b2->age
}
")
```

### Multi-level v2

For example you might think that generally individuals that ...

$$ outcome = \beta_0 + \beta_1(sex_i) + \beta(age_i) + error_i $$

```{r echo=FALSE}
grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica]
  b0; b1; b2; error

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  sex; age; 
  
  # several 'edge' statements
  b1->sex; b2->age
}
")
```

